Target Readability in Interpersonal Accuracy

### 2022-05-16 manuscript.Rmd
update results section's structure

```{r message=FALSE, include=FALSE, results='hide'}
library(tidyverse)
```

@@

## Descriptive statistics
```{r}
descriptive_df <-
df %>% 
  select(
    InsecAtt, AnxAtt, AvoAtt, Authenticity, Mask, NTB, Loneliness,
    FNE, beqpos, beqneg, beqstr, erqsup, erqrea, RSE, SAT, POW,
    SIAS, SPS, SIAPS, Extr, Agree, Consc, Neurot, Open
  )

@@

## Aim 1
### Examine variance decomposition in interpersonal accuracy and compare across accuracy measures

@@

```{r}
# personality traits
samdata <- import(here("data", "asd.csv"))

library(lme4)
library(lmerTest)
options(digits=5)

samdata$Avgtrait <- samdata$Avgtrait - 1

samdata$targSRr <- samdata$targSR - samdata$Avgtrait

samdata$targSRrC <- samdata$targSRr -0.0003679
samdata$AvgtraitC <- samdata$Avgtrait - 4.0317762737
samdata$ptraitC <- samdata$ptrait - 3.5820554

null1 <- lmer (ptrait ~ (1|PerUn) + (1|TarUn) + (1|DyUn) + (1|Group), data=samdata)
summary (null1)

samdat1 <- lmer (ptrait ~ (1|PerUn) + (1|TarUn) + (1|DyUn) + (1|Group), data=samdata)
summary (samdat1)

@@

## Aim 2
### Examine interrelations among target readability estimates for different measures of interpersonal accuracy

In order to examine interrelations among target readability estimates for different measures of interpersonal accuracy, the Empirical Bayes random target effect estimates were extracted from the analysis of the baseline models for each outcome measure (when target variance was nonzero).

@@

## Aim 3
### Investigate potential individual differences that correlate with target readability as well as look for patterns of individual differences that consistently correlate with readability across measures

Based on guiding hypotheses generated from Funder’s RAM and previous research regarding target readability, individual differences linked to expressivity, social threat sensitivity, and psychological adjustment were measured. In order to investigate whether any of these measures correlated with target readability, I computed correlations between the Empirical Bayes random target effects extracted from the baseline models estimated in Aim 1 and the individual difference variables (assessed via self-reports and informant-reports). Table X displays these correlations separately for self-reports and informant-reports alongside 95% confidence intervals.

>>>>

```{r message=FALSE, include=FALSE, results='hide'}
library(tidyverse)
library(lme4)
library(lmerTest)
```

@@

## Descriptive statistics for Empathic Accuracy
```{r}
descriptive_df <-
df %>% 
  select(
    InsecAtt, AnxAtt, AvoAtt, Authenticity, Mask, NTB, Loneliness,
    FNE, beqpos, beqneg, beqstr, erqsup, erqrea, RSE, SAT, POW,
    SIAS, SPS, SIAPS, Extr, Agree, Consc, Neurot, Open
  )

@@

## Interpersonal accuracy for thoughts, affect, and personality traits

@@

```{r}
# personality traits
samdata <- import(here("data", "samdata.csv"))

@@

## Variance decomposition in interpersonal accuracy for thoughts, affect, and personality traits

@@

## Predictors of interpersonal accuracy
